Excuse me, do you have a moment to talk about version control?

### 2017-07-07 README.Rmd
https

Why would a statistician use a version control system, such as [Git](http://git-scm.com) [@git]? And what is the point of hosting your work online, e.g., on [GitHub](https://github.com) [@github]? Could the gains possibly justify the inevitable pain?

>>>>

Why would a statistician use a version control system, such as [Git](https://git-scm.com) [@git]? And what is the point of hosting your work online, e.g., on [GitHub](https://github.com)[@github]? Could the gains possibly justify the inevitable pain?
